Douglas-complex fire smoke and cardiopulmonary morbidity

### 2017-11-14 r_scripts/analysis/oregon_cvd_pulm_results.Rmd

##4. Distributed lag cumulative effect results

@@

# will put this table eventually
head(cumulative_results)

# ggplot ----
plot <- ggplot(cumulative_results, aes(x=outcome_names, y = estimate)) +
  geom_point(colour = "darkblue") +
  geom_text(aes(label = round(estimate,2)), hjust = -0.25) +
  geom_errorbar(aes(ymin=lower95, ymax=upper95), 
                colour= "darkblue", width = 0.2) +
  geom_hline(yintercept = 1, linetype = 2, colour = "red") +
  theme(
   panel.background = element_rect(fill = 'white', colour = 'black'),
   panel.grid.major = element_blank(),
   panel.grid.minor = element_blank(),
   axis.text.x = element_text(angle=90, hjust = 1)) +
  ylab(expression(paste0("Cumulative odds ratio for a 10 ug/m"^3, 
    " increase smoke PM"[2.5]))) +
  xlab("Outcomes")

@@

##5. Distributed lag results

@@

```{r distributed lag}
# this approach will work that creates a list of dataframes with map then
# binds the lists together in one dataframe
dl_results <- outcome_df_list %>% 
  purrr::map(~distributed_lag(., pm_df=3, temp_df=2, cumulative=F)) %>% 
  plyr::rbind.fill() %>% 
  bind_cols(., data_frame(rep(outcome_names, each=8))) %>% 
  rename(outcome_names = `rep(outcome_names, each = 8)`) %>% 
  select(outcome_names, type, time, estimate, lower95, upper95)

# results will come in a format to make small multiples I think
head(dl_results)

# small multiples DL plot ----
dl_plot <- ggplot(dl_results, aes(x=time, y=estimate)) +
  geom_line(colour = "#046C9A", size = 1) +
  geom_ribbon(aes(ymin = lower95, ymax = upper95), 
              fill = "#ABDDDE", alpha = 0.5) + 
  scale_y_continuous(limits = c(0.9, 1.15)) +
  scale_x_continuous(breaks = c(seq(-7, 0, by=1))) +
  geom_hline(yintercept = 1, linetype = 2, colour = "red") +
  facet_wrap(~outcome_names, scales = "free_x") +
  ylab(expression("Odd ratio for a 10 ug/m^3 increase smoke PM"[2.5])) +
  xlab("Lagged Days") +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    strip.text = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_rect(colour=NA, fill=NA))

@@

##6. Stratified cumulative results

@@

##7. SABA cumulative effect by underlying respiratory diagnosis
*Jingyang to complete using function*

>>>>

##4. Same-day association results

*Jingyang, add same day associations here using purrr map functions here. I want to compare them to the cumulative associations. You do not need to make an elaborate function like I did for the distributed lag. You should just be able to use clogit. Include the same day GWR smoke estimate and same day temperature as a covariate.*

##5. Distributed lag cumulative effect results

@@

# will put this table eventually and split out plot
#head(cumulative_results)

# ggplot ----
plot <- ggplot(cumulative_results, aes(x=outcome_names, y = estimate)) +
  geom_point(colour = "darkblue") +
  geom_text(aes(label = round(estimate,2)), hjust = -0.25) +
  geom_errorbar(aes(ymin=lower95, ymax=upper95), 
                colour= "darkblue", width = 0.2) +
  geom_hline(yintercept = 1, linetype = 2, colour = "red") +
  theme(
   panel.background = element_rect(fill = 'white', colour = 'black'),
   panel.grid.major = element_blank(),
   panel.grid.minor = element_blank(),
   axis.text.x = element_text(angle=90, hjust = 1)) +
  ylab(expression("Cumulative odds ratio: 10 ug/m^3 increase smoke PM"[2.5])) +
  xlab("Outcomes")

@@

##6. Distributed lag results

@@

```{r distributed lag}
# this approach will work that creates a list of dataframes with map then
# binds the lists together in one dataframe
dl_results <- outcome_df_list %>% 
  purrr::map(~distributed_lag(., pm_df=3, temp_df=2, cumulative=F)) %>% 
  plyr::rbind.fill() %>% 
  bind_cols(., data_frame(rep(outcome_names, each=8))) %>% 
  rename(outcome_names = `rep(outcome_names, each = 8)`) %>% 
  select(outcome_names, type, time, estimate, lower95, upper95) %>% 
  # preserve order of names
  mutate(outcome_names = parse_factor(outcome_names, levels = outcome_names))

# results will come in a format to make small multiples I think
#head(dl_results)

# small multiples DL plot ----
dl_plot <- ggplot(dl_results, aes(x=time, y=estimate)) +
  geom_line(colour = "#046C9A", size = 1) +
  geom_ribbon(aes(ymin = lower95, ymax = upper95), 
              fill = "#ABDDDE", alpha = 0.5) + 
  scale_y_continuous(limits = c(0.8, 1.2)) +
  scale_x_continuous(breaks = c(seq(-7, 0, by=1))) +
  geom_hline(yintercept = 1, linetype = 2, colour = "red") +
  facet_wrap(~outcome_names) +
  ylab(expression("Odd ratio for a 10 ug/m^3 increase smoke PM"[2.5])) +
  xlab("Lagged Days") +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    strip.text = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_rect(colour=NA, fill=NA))

@@

##7. Stratified cumulative results

@@

##8. SABA cumulative effect by underlying respiratory diagnosis
*Jingyang to complete using function*
